                              Assignment: Exercise 1-2
Get familiar to environmental (or your related field) data.Collect three (or more)
sets of environmental or experimental data. Number of samples in each data set (n) should be more than 100. 
Then, report the following information on the collected data.
1. Background and data source
2. Raw data with units
3. Central tendency(Arithmetic Mean, Geometric Mean, Median, Mode)
4. Variability(Range, Variance, Standard Deviation, Coefficient of Variation)

Solution:
1. Background and data source
https://vincentarelbundock.github.io/Rdatasets/datasets.html

2. Raw data with units

Title: Sleep Hours for Teenagers

Units: Person, Age, Outcome

Number of samples: 446

3. Central tendency(Arithmetic Mean, Geometric Mean, Median, Mode)
```{r}
sleep<-read.csv("LosingSleep.csv")
print(sleep)

#Arithmetic Mean
print(mean(sleep$Age))
print(mean(sleep$Person))
print(mean(sleep$Outcome))

#Geometric Mean
length(sleep$Person)
x<-1/(length(sleep$Person))
x
prod(sleep$Age)
prod(sleep$Person)^(1/length(sleep$Person))
prod(sleep$Age)^(1/length(sleep$Age))
prod(sleep$Outcome)^(1/length(sleep$Outcome))

#median
median(sleep$Person) 
median(sleep$Age)
median(sleep$Outcome)

#mode

m <- names(sleep$Person)[which(sleep$Person == max(sleep$Person))] 
print(m)

a <- names(sleep$Age)[which(sleep$Age == max(sleep$Age))] 
print(a)
b <- names(sleep$Outcome)[which(sleep$Outcome == max(sleep$Outcome))] 
print(b)

```

4. Variability(Range, Variance, Standard Deviation, Coefficient of Variation)
```{r}
# Range
print(range(sleep$Person))
print(max(sleep$Person) - min(sleep$Person))

print(range(sleep$Age))
print(max(sleep$Age) - min(sleep$Age))

print(range(sleep$Outcome))
print(max(sleep$Outcome) - min(sleep$Outcome))
#Variance
print(var(sleep$Person))
print(var(sleep$Age))
print(var(sleep$Outcome))

#standard Deviation
print(sqrt(var(sleep$Person)))
print(sqrt(var(sleep$Age)))
print(sqrt(var(sleep$Outcome)))

#Coefficient of Variation
print((sqrt(var(sleep$Person)))/mean(sleep$Person))
print((sqrt(var(sleep$Age)))/mean(sleep$Age))
print((sqrt(var(sleep$Person)))/mean(sleep$Age))



```



